2019 Draft Prep

### 2019-03-23 draftPrep.Rmd
Functioning cheat sheet app, though working on a minor bug or two

```{r echo=FALSE}
batters_ranked %>%
  select(Name, z_rank, z_sum, ADP, positions) -> batters_draft

@@

pitchers_ranked %>%
  select(Name, z_rank, z_sum, ADP, positions) -> pitchers_draft

@@

pitchers_draft %>%
  bind_rows(batters_draft) %>%
  mutate(round = ceiling(ADP/12)) %>%
  arrange(z_sum %>% desc) %>%
  mutate(z_rank = row_number()) %>%
  select(z_rank, Name, z_sum, round, ADP, positions) -> draft_df

@@

draft_df %>%
  head(25) %>%
  kable()
```

>>>>

```{r echo=FALSE}
batters_ranked %>%
  select(Name, z_rank, z_sum, ADP, positions, display_position) -> batters_draft

@@

pitchers_ranked %>%
  select(Name, z_rank, z_sum, ADP, positions, display_position) -> pitchers_draft

@@

pitchers_draft %>%
  bind_rows(batters_draft) %>%
  mutate(round = ceiling(ADP/12),
         keeper = (Name %in% keepers)) %>%
  filter(!keeper) %>%
  arrange(z_sum %>% desc) %>%
  mutate(z_rank = row_number()) %>%
  select(z_rank, Name, z_sum, round, ADP, positions, display_position) -> draft_df

@@

draft_df %>%
  select(-display_position) %>%
  head(25) %>%
  kable()
```
